Ornaments as indicators of social changes in northeastern Taiwan before and after the European colonial period

### 2020-04-21 analysis/paper/paper.Rmd
update the ornament image

```{r, ornaments-image, fig.cap = "Subtypes of ornament in each major class. A: carnelian beads, B: bells, C: glass beads (the far left and the middle) and gold-foil beads (the far right), D: metal rings. Photographs are presented in the same order as those subtypes in the table but from left to right instead. The photographs of B, C, D classes were from original excavation report (Chen 2007)", echo=FALSE}
knitr::include_graphics(here("analysis", "figures", "ornament.png"))
```

>>>>

```{r, ornaments-image, fig.cap = "Subtypes of ornament in each major class. A: carnelian beads, B: glass beads, C: gold-foil beads, D: bells, E: metal rings. Photographs are presented in the same order as those subtypes in the table but from left to right instead. The photographs of B, C, D, E classes were from original excavation report (Chen 2007)", echo=FALSE}
knitr::include_graphics(here("analysis", "figures", "ornament_edit.png"))
```
